---
title: "Day 2 Activity"
author: "Dana Seidel & Eric Dougherty"
date: "1/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Find and load unique movement data. This can be some of your own, or some pulled from movebank, any other online source, or example data pulled from R packages. 

```{r}
loginStored <- movebankLogin(username="tcaspi", password=pass)

#get study ID - 
getMovebankStudy(236023, login=loginStored)$citation

#check for animal IDs - 
getMovebankAnimals(236023, login=loginStored)

carnivores <- getMovebankData(study = 236023, login = loginStored)

class(carnivores)
```


```{r}
loginStored <- movebankLogin(username="tcaspi", password=pass)

#get study ID - 
getMovebankStudy(10857031, login=loginStored)$citation

#check for animal IDs - 
getMovebankAnimals(10857031, login=loginStored)

cats <- getMovebank("event", study_id = 10857031, login=loginStored)
class(cats)
ncats <- unique(cats$individual_id)
length(ncats) #155 unique cats

cats$timestamp <- as.POSIXct(cats$timestamp, format = "%Y-%m-%d %H:%M:%S" ) #format timestamp into datetime
cats <- cats %>% na.omit() #remove NAs
```

2. Build a regular ltraj object and plot distributions of turning angles and 
step lengths for each individual in your dataset

```{r}

carnivores.df <- as.data.frame(carnivores)
coyotes.df <- carnivores.df %>% 
  filter(taxon_canonical_name == "Canis latrans") 
coyotes.df2 <- coyotes.df[, c("timestamp", "tag_id", "location_lat", "location_long", "individual_id")]
coyotes.df2 <- na.omit(coyotes.df2)

coyotes_sf <- 
  coyotes.df2 %>% na.omit() %>%
  st_as_sf(coords = c("location_long", "location_lat"), crs=4326)

coyotes_sf %>% 
  group_by(individual_id) %>% 
  tally()

coyotes_mov <- move(x=coyotes.df2$location_long,
              y=coyotes.df2$location_lat,
              time=coyotes.df2$timestamp,
              data=coyotes.df2,
              animal = as.factor(coyotes.df2$individual_id),
              sensor = as.factor(coyotes.df2$tag_id),
              proj=CRS("+proj=longlat"))

coyotes_ltraj  <- as(coyotes_mov, 'ltraj')
coyotes_ltraj

unq_id <- unique(coyotes.df2$individual_id)
n <- length(unq_id)

hist(coyotes_ltraj[1], "dt", freq = T)
hist(coyotes_ltraj[9], "dt", freq = T)

median(coyotes_ltraj[[1]]$dt, na.rm = T) #supposed to take a fix every 3 minutes (180 seconds)
median(coyotes_ltraj[[2]]$dt, na.rm = T)
median(coyotes_ltraj[[6]]$dt, na.rm = T)
median(coyotes_ltraj[[10]]$dt, na.rm = T)


#Step lengths distributions WITHOUT turning to regular trajectory
hist(coyotes_ltraj[[1]]$dist)
hist(coyotes_ltraj[[2]]$dist)
hist(coyotes_ltraj[[3]]$dist)
hist(coyotes_ltraj[[4]]$dist)
hist(coyotes_ltraj[[5]]$dist)
hist(coyotes_ltraj[[6]]$dist)
hist(coyotes_ltraj[[7]]$dist)
hist(coyotes_ltraj[[8]]$dist)
hist(coyotes_ltraj[[9]]$dist)
hist(coyotes_ltraj[[10]]$dist)

#Turning angles
hist(coyotes_ltraj[[1]]$rel.angle)
hist(coyotes_ltraj[[2]]$rel.angle)
hist(coyotes_ltraj[[3]]$rel.angle)
hist(coyotes_ltraj[[4]]$rel.angle)
hist(coyotes_ltraj[[5]]$rel.angle)

```


```{r}
#creating a Movestack object
cats.mov <- move(x=cats$location_long,
              y=cats$location_lat,
              time=cats$timestamp,
              data=cats,
              animal = as.factor(cats$individual_id),
              sensor = as.factor(cats$tag_id),
              proj=CRS("+proj=longlat"))

cat_ids <- split(cats.mov)

cats_ltraj  <- as(cats.mov, 'ltraj') #creating the ltraj object
cats_ltraj  #irregular type II 

#Figuring out what to correct to to make regular
hist(cats_ltraj[1], "dt", freq = T)
hist(cats_ltraj[2], "dt", freq = T)
hist(cats_ltraj[3], "dt", freq = T)
hist(cats_ltraj[4], "dt", freq = T)
hist(cats_ltraj[5], "dt", freq = T)

median(cats_ltraj[[1]]$dt, na.rm = T) #supposed to take a fix every 3 minutes (180 seconds)
median(cats_ltraj[[2]]$dt, na.rm = T)
median(cats_ltraj[[3]]$dt, na.rm = T)
median(cats_ltraj[[4]]$dt, na.rm = T)
median(cats_ltraj[[5]]$dt, na.rm = T)

#Cat 1 setting regulat
cat1_raw <- cats_ltraj[1]
cat1_raw[[1]]$date <- lubridate::force_tz(cat1_raw[[1]]$date, "EST") # hack to simplify timezones.

## The reference date: the hour should be exact (i.e. minutes=0):
ref <- strptime("00:00:00", "%H:%M:%S", tz="EST")

cat1_raw %>% 
  setNA(., ref, 3, units = "min") %>%  # set the missing values
  sett0(., ref, 3, units = "min") -> cat1   # round the fixes to 3 min 

is.regular(cat1)

#Cat 2
cat2_raw <- cats_ltraj[2]
cat2_raw[[1]]$date <- lubridate::force_tz(cat2_raw[[1]]$date, "EST")

cat2_raw %>% 
  setNA(., ref, 3, units = "min") %>%  
  sett0(., ref, 3, units = "min") -> cat2  

is.regular(cat2)

#Cat 3
cat3_raw <- cats_ltraj[3]
cat3_raw[[1]]$date <- lubridate::force_tz(cat3_raw[[1]]$date, "EST")

cat3_raw %>% 
  setNA(., ref, 3, units = "min") %>%  
  sett0(., ref, 3, units = "min") -> cat3  

is.regular(cat3)

#Step Lengths

cat1$dist

cats_ltraj[100]$dist

ibex[[1]]$dist

hist(cats_ltraj[[1]]$dist)

```

3. Find an appropriate raster from an online data source. Below are a few options 
to help you get started, alternatively just search "global gis data" or similar:
  - https://earthexplorer.usgs.gov/
  - https://www.movebank.org/node/7471
  - https://earthworks.stanford.edu/
  - http://gisgeography.com/best-free-gis-data-sources-raster-vector/

4. Load and project raster into R. Remember you may need to crop, or transform your raster 
to match your vector data. 

5. Extract, intersect, or spatially join your raster values to your movement 
data points and form a clean data.frame. 

6. Using dpylr verbs, filter those points based upon some interesting limits of 
your extracted values. For instance, if your raster is elevation, filter points 
above or below, or between certain elevation levels. 

7. Visualize the movement points with a custom map using ggplot with geom_sf or mapview 