---
title: 'Day 3: Home Range Activity'
author: "Eric Dougherty & Dana Seidel"
date: "1/5/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Choose movement data of your own or from a package. 

```{r}
library(tidyverse)
library(sf)
library(mapview)
library(move)
library(adehabitatLT)
library(adehabitatHR)
library(tlocoh)
library(ggplot2)

loginStored <- movebankLogin(username="tcaspi", password=pass)
getMovebankStudy(2911040, login=loginStored)$citation
getMovebankAnimals(2911040, login=loginStored) #checking for animal ids

#getting data for only one individual
albatross <- getMovebank("event", study_id = 2911040, login=loginStored, individual_id = 2911059)
albatross <- na.omit(albatross)

```

2. Build a 100% MCP, 100% KDE_UD, 100% LoCoH_UD

# Minimum Convex Polygon 
```{r}
lat_long <- SpatialPoints(na.omit(albatross)[,2:3])

mcp <- mcp(lat_long, percent = 100)

mcp_sf <- st_as_sf(mcp)
lat_long_sf <- st_as_sf(lat_long)

ggplot() + geom_sf(data = mcp_sf) + geom_sf(data = lat_long_sf)
```

#Kernel Density Estimate
```{r}
kud <- kernelUD(lat_long)  # h = href is the default - ad hoc method for determining h
image(kud) + title("Albatross UD")

k.area <- kernel.area(kud)
plot(k.area)
ver100 <- getverticeshr(kud) #getting the contours at 100%
plot(ver100) + points(lat_long) #plot contours and GPS points
```

#Loco-H (100%)
```{r}
#first need to project coordinates into UTM
albatross.sp.latlong <- SpatialPoints(na.omit(albatross[, c("location_lat", "location_long")]), proj4string = CRS("+proj=longlat +ellps=WGS84"))
albatross.sp.utm <- spTransform(albatross.sp.latlong, CRS("+proj=utm +south +zone=15 +ellps=WGS84"))

albatross.sp.utm <- spTransform(albatross.sp.latlong,CRS("+proj=laea +ellps=WGS84 +lon_0=147 +lat_0=-42"))

albatross.mat <- coordinates(albatross.sp.latlong)

#~~~

#set time in datetime format
albatross.tz <- as.POSIXct(albatross$timestamp, tz = "Pacific/Galapagos")
toni.gmt <- as.POSIXct(toni$timestamp.utc, tz="UTC")

#create the lxy object
albatross.lxy <- xyt.lxy(xy = albatross.mat, dt = albatross.tz, id = "2911059" , proj4string = CRS("+proj=longlat +ellps=WGS84"))
summary(albatross.lxy)
hist(albatross.lxy)
lxy.plot.freq(albatross.lxy, cp=T)
albatross.lxy <- lxy.thin.bursts(albatross.lxy, thresh=0.99)

#setting k nearest neighbors
albatross.lxy <- lxy.nn.add(albatross.lxy, s=0, k=30)
summary(albatross.lxy)
#create hull sets with different values of k
albatross.lhs <- lxy.lhs(albatross.lxy, k=3*1:10, s=0)
plot(albatross.lhs, hulls=TRUE, figs.per.page=6)
#create isopleths to reflect likelihood of occurence; specifically create 100% isopleth
albatross.lhs <- lhs.iso.add(albatross.lhs, iso.levels=c(0.5, .95, 1))
plot(albatross.lhs, iso=TRUE, figs.per.page=6)
#take a closer look at selected homerange
plot(albatross.lhs, iso=T, k=30, allpts=T, cex.allpts=0.1, col.allpts="gray30", ufipt=F)

#plot isopleth area curves
lhs.plot.isoarea(albatross.lhs) #at 30, the curve flattens out
lhs.plot.isoear(albatross.lhs) #curve flattens out by ~10, but in the previous plot, not until k = 30

#select the k value
albatross.lhs.k30 <- lhs.select(albatross.lhs, k=30)

```


3. Plot home range area vs. percentage isopleth to see the relationship in your spatial data and how the separate home range estiamtors differ. (Similar to the output of `mcp.area` or `kernel.area`)

```{r}

plot(albatross.lhs.k30, allpts = T, hulls = T)
plot(albatross.lhs.k30, iso = T)

#extract isopleth polygons
albatross.isos <- isopleths(albatross.lhs.k30)
class(albatross.isos[[1]])
albatross.isos[[1]]@data

albatross.isos[[1]]

albatross.hr <- albatross.isos[[1]][albatross.isos[[1]][["iso.level"]]==0.95, ]
albatross.core <- albatross.isos[[1]][albatross.isos[[1]][["iso.level"]]==0.5, ]
class(albatross.hr)
plot(albatross.hr, border="blue")  
plot(albatross.core, border="red")

albatross.hr@polygons[[1]]@area

```

4. Try comparing outputs of k-LoCoH and a-LoCoH

LoCoH.k(xy, k=5, unin = c("m", "km"),
        unout = c("ha", "m2", "km2"),
        duplicates=c("random","remove"), amount = NULL)

LoCoH.a(xy, a, unin = c("m", "km"),
        unout = c("ha", "m2", "km2"),
        duplicates=c("random","remove"), amount = NULL)

5. Try comparing across smoothing parameters and/or other kernel and hull methods found in the adehabitatHR library

6. Adapt your code to run across multiple individuals or datasets, see what you can infer about animal life history behavior from home range size and shape. 